---
title: "An example of the use of Mapview"
output:
  html_document:
    df_print: paged
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

This is a just a quick example on how to use the mapview package. It's not a tutorial ... just an example.

The [mapview basics](https://r-spatial.github.io/mapview/articles/articles/mapview_01-basics.html) tutorial helped me figure out the basics. [A Quick Start to Maps in R](https://medium.com/fastah-project/a-quick-start-to-maps-in-r-b9f221f44ff3) helped me figure out how to find lat/long from a dataset and include it for the map.

```{r setup, echo=T, results='hide', message=F, warning=F}
library(mapview)
library(tidyverse)
library(sp)
```

## Using mapview to show some wells

Importing wells

```{r}
wells <- read_rds("data-raw/wells_03.rds")
```

Looking at the use_clean column just to inspect them.

```{r}
wells %>% 
  count(use_clean)
```

Filtering on just the irrigation wells in Travis county just to reduce the number of wells to plot.

```{r}
wells_trav_irr <- wells %>% 
  filter(county == "Travis",
         use_clean == "irrigation")
```

This is the bit to map the wells. 

```{r}
coordinates(wells_trav_irr) <- ~ coord_dd_long + coord_dd_lat
proj4string(wells_trav_irr) <- "+init=epsg:4326"

mapview(wells_trav_irr)
```